A Blockchain Consensus Protocol with\\Horizontal Scalability

### 2018-05-16 conference-presentation/presentation.tex
Final tweaks

\section{System architecture}
\begin{frame}{Intuition and idea explored in this thesis}
  \begin{itemize}
    \item It is expensive to verify and reach consensus on all transactions
    \item Our idea: we decouple consensus and validation
    \item A single digest represents an arbitrarily large number of transactions
    \item Reach consensus on the small digest
    \item Nodes then independently check the validity of the transactions of interest
  \end{itemize}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{idea}
  \centering
  \end{figure}
\end{frame}

\subsection{System model}
\subsection{Architecture overview}
\begin{frame}{\subsecname}
  \begin{center}
  {\Large The four components of \textsc{Checo}\footnote{\textsc{Che}ckpoint \textsc{co}nsensus}} 
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{architecture-wo-title}
  \centering
  \end{figure}
  \end{center}
  \note{
    \begin{itemize}
    \item The primary data structure is the Extended TrustChain, extension of our prior work
    \item The three protocols the tasks as their name suggests
    \item They are independent and run concurrently
    \item The only synchronisation happens via the Extended TrustChain
    \item But in no part of those protocol do we lock the Extended TrustChain
    \end{itemize}
  }
\end{frame}

@@

\subsection{Transaction protocol}
\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=1.0\textwidth]{tx-proto}
  \centering
  \end{figure}
\begin{itemize}
\item Two TX blocks are generated on the chains of Alice and Bob
\item No guarantee that nodes follow this protocol
\item Contrary to early blockchain systems, we do not broadcast transactions
\end{itemize}
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\emph{Consensus on CP blocks $\rightarrow$ consensus on transactions}
\bigskip
\begin{itemize}
  \item CP blocks of the fragments are ``anchored'' due to the consensus protocol
  \item It is difficult to modify the fragment once ``anchored''
  \item Since the transaction protocol and the validation protocol only use point-to-point communication,
  we achieve horizontal scalability.
\end{itemize}
\end{frame}

@@

\section{Conclusion}
\begin{frame}{\secname}
    Our contribution:
  \begin{itemize}
      \item We design a blockchain consensus protocol---\textsc{Checo} with horizontal scalability
      \item We formally analyse CHECO to ensure correctness
      \item Our experimental evaluation show strong evidence of our claim.
  \end{itemize}
      Future perspective:
  \begin{itemize}
      \item Improve fault-tolerance using ByzCoinX from OmniLedger
      \item Design and evaluate UTXO-style transactions (new paper to appear in Crypto Valley Conference)
      \item Assume a permissionless model
  \end{itemize}
\end{frame}

>>>>

\section{System architecture}
\begin{frame}{Intuition}
  \begin{itemize}
    \item It is expensive to verify and reach consensus on all transactions
    \item Our idea: we decouple consensus and validation
    \item A single digest represents an arbitrarily large number of transactions
    \item Reach consensus on the small digest
    \item Nodes then independently check the validity of the transactions of interest
  \end{itemize}
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{idea}
  \centering
  \end{figure}
\end{frame}

\subsection{Architecture overview}
\begin{frame}{\subsecname}
  \begin{center}
  {\Large The four components of \textsc{Checo}\footnote{\textsc{Che}ckpoint \textsc{co}nsensus}} 
  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{architecture-wo-title}
  \centering
  \end{figure}
  \end{center}
  \note{
    \begin{itemize}
    \item The primary data structure is the Extended TrustChain, extension of our prior work
    \item The three protocols the tasks as their name suggests
    \item They are independent and run concurrently
    \item The only synchronisation happens via the Extended TrustChain
    \item But in no part of those protocol do we lock the Extended TrustChain
    \end{itemize}
  }
\end{frame}

@@

\subsection{Transaction protocol}
\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=1.0\textwidth]{tx-proto}
  \centering
  \end{figure}
\begin{itemize}
\item Two TX blocks are generated on the chains of Alice and Bob
\item Contrary to early blockchain systems, we do not broadcast transactions
\item No guarantee that nodes follow this protocol
\end{itemize}
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\emph{Consensus on CP blocks $\rightarrow$ consensus on transactions}
\bigskip
\begin{itemize}
  \item CP blocks of the fragments are ``anchored'' due to the consensus protocol
  \item It is not possible to modify the fragment once ``anchored''
  \item Since the transaction protocol and the validation protocol only use point-to-point communication,
  we achieve horizontal scalability.
\end{itemize}
\end{frame}

@@

\section{Conclusion}
\begin{frame}{\secname}
    Our contribution:
  \begin{itemize}
      \item We design a blockchain consensus protocol---\textsc{Checo} with horizontal scalability
      \item We formally analyse \textsc{Checo} to ensure correctness
      \item Our experimental evaluation show strong evidence of our claim.
  \end{itemize}
      Future perspective:
  \begin{itemize}
      \item Improve fault-tolerance using ByzCoinX from OmniLedger
      \item Design and evaluate UTXO-style transactions (new paper to appear in the Crypto Valley Conference)
      \item Assume a permissionless model
  \end{itemize}
\end{frame}
